---
title: " "
author: " "
date: ' '
output:
  html_document
runtime: shiny
---

```{r include=FALSE}
library(visNetwork)
library(igraph)
library(r2d3)
library(kableExtra)
library(dplyr)
library(shiny)
library(shinythemes)
library(DT)
```

<br>

# Consistently estimating network statistics using *Aggregated Relational Data* (***ARD***): A Primer
The full paper can be found [here](https://arxiv.org/abs/1908.09881).

<br>

### Collecting complete network data is expensive, time-consuming, and often infeasible. 

### ***ARD*** captures network information by asking a respondent questions of the form:

<br>

<center> <font size="5">  ***How many people with trait X do you know?*** </font>  </center>

<br>

### Researchers can use this relatively low-cost data to estimate features of the complete network when it cannot be directly observed.

### Here's how it works.

<br>

### Assume the population of interest consists of 10 nodes, and each node belongs to one of two groups (Red or Gold). In this setting, ***group status cannot be directly observed by the researcher.*** 

```{r, echo=FALSE}

#dataset
nodes = data.frame(id = 1:10,
                  label = as.character(1:10),
                  shape = "dot",
                  size = 25, 
                  font.size = 25,
                  align = "center",
                  group = c(rep("Red", 5), 
                            rep("Gold", 5)),
                  borderWidth = 2,
                  color.background = c(rep("tomato", 5), 
                                       rep("gold", 5)),
                  color.border = "black",
                  color.highlight.background = "green", 
                  color.highlight.border = "black",
                  shadow = TRUE
                  # title = paste0("</b>Node </p>", 1:10)
)

visNetwork(nodes)
```

### Nodes in this network form edges with a connection probability such that nodes of the ***same group*** are ***more likely*** to connect. 

### Let $G$ represent the complete, unobserved network. 

```{r, echo=FALSE}

#dataset
nodes = data.frame(id = 1:10,
                  label = as.character(1:10),
                  shape = "dot",
                  size = 30, 
                  font.size = 25,
                  align = "center",
                  group = c(rep("Red", 5), 
                            rep("Gold", 5)),
                  borderWidth = 2,
                  color.background = c(rep("tomato", 5), 
                                       rep("gold", 5)),
                  color.border = "black",
                  color.highlight.background = "green", 
                  color.highlight.border = "black",
                  shadow = TRUE
                  # title = paste0("</b>Node </p>", 1:10)
)

edges = data.frame(from = c(1, 2, 3, 3, 4, 4, 5, 6, 6, 7, 8, 9, 10),
                  to   = c(3, 3, 4, 5, 5, 6, 7, 2, 8, 8, 9, 10, 8))

visNetwork(nodes, edges)
```

### Finally, each node has a specific trait illustrated by different shapes (circle, triangle or square).

### We assume that these observable traits are associated with latent group status, but not perfectly. 

```{r, echo=FALSE}

#dataset
nodes = data.frame(id = 1:10,
                  label = as.character(1:10),
                  shape = c("star", 
                            "triangle",
                            "triangle", 
                            "triangle",
                            "square", 
                            "triangle",
                            "square", 
                            "star",
                            "square", 
                            "square"),
                  size = 30, 
                  font.size = 25,
                  align = "center",
                  group = c(rep("Red", 5), 
                            rep("Gold", 5)),
                  borderWidth = 2,
                  color.background = c(rep("tomato", 5), 
                                       rep("gold", 5)),
                  color.border = "black",
                  color.highlight.background = c(rep("Tomato", 5), 
                                                 rep("Gold", 5)),
                  color.highlight.border = "black",
                  shadow = TRUE
                  # title = paste0("</b>Node </p>", 1:10)
)

edges = data.frame(from = c(1, 2, 3, 3, 4, 4, 5, 6, 6, 7, 8, 9, 10),
                  to   = c(3, 3, 4, 5, 5, 6, 7, 2, 8, 8, 9, 10, 8))

visNetwork(nodes, edges)
```

### Asking each node $i$ in $G$ how many of their neighbors have a given trait yields ARD response $y_i$.

<br>

<center> <font size="5">  ***Click on a node to see its ARD response $y_i$!*** </font>  </center>

```{r, echo=FALSE}

#dataset
nodes = data.frame(id = 1:10,
                  label = as.character(1:10),
                  shape = c("star", 
                            "triangle",
                            "triangle", 
                            "triangle",
                            "square", 
                            "triangle",
                            "square", 
                            "star",
                            "square", 
                            "square"),
                  size = 25, 
                  font.size = 25,
                  align = "center",
                  group = c(rep("Red", 5), 
                            rep("Gold", 5)),
                  borderWidth = 2,
                  color.background = c(rep("tomato", 5), 
                                       rep("gold", 5)),
                  color.border = "black",
                  color.highlight.background = c(rep("Tomato", 5), 
                                                 rep("Gold", 5)),
                  color.highlight.border = "black",
                  shadow = TRUE
                  # title = paste0("</b>Node </p>", 1:10)
)

edges = data.frame(from = c(1, 2, 3, 3, 4, 4, 5, 6, 6, 7, 8, 9, 10),
                  to   = c(3, 3, 4, 5, 5, 6, 7, 2, 8, 8, 9, 10, 8))

# how many each node knows data
ARD = data.frame(rbind(c(1, 0, 1, 0),
                       c(2, 0, 2, 0),
                       c(3, 1, 2, 1),
                       c(4, 0, 2, 1),
                       c(5, 0, 2, 1),
                       c(6, 1, 2, 0),
                       c(7, 1, 0, 1),
                       c(8, 0, 1, 3),
                       c(9, 1, 0, 1),
                       c(10, 1, 0, 1)))
colnames(ARD) = c("Node", "Star", "Triangle", "Square")

ui = fluidPage(
    dataTableOutput("nodes_data_from_shiny", width="100%"),
    visNetworkOutput("network_proxy", height = "600px")
)

server = function(input, output, session) {

  # highlight selected node and contacts
  output$network_proxy = renderVisNetwork({
    visNetwork(nodes, edges) %>%
      visOptions(highlightNearest=TRUE) %>%
      
      visEvents(select = "function(nodes) {
                Shiny.onInputChange('current_node_id', nodes.nodes);
                ;}")
  })
  
  # display output from ARD table based on node selection
  output$nodes_data_from_shiny = renderDT({
    info = data.frame(ARD)
    
    info[ARD$Node == input$current_node_id, ]
  }, 
  
  # only display table, not search or page toggle
  options = list(dom = 't'),
  rownames = FALSE)

}

shinyApp(ui, server, options = list(height = 725))
```

### Remember how we assumed that observable traits are associated with latent group membership? We can use this assumption to take the ARD responses to classify group status for each node $i$. 

### For example, if ARD response $y_i$ knows multiple squares, node $i$ is probably part in the ***Yellow*** community. On the other hand, if $y_i$ knows multiple triangles, node $i$ probably belongs to ***Red***.

### Combining ARD responses $y_i$ yields the following ARD table, $Y$.

<br>

```{r, echo = FALSE}
ARD %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = T)
```

### $Y$ is used to fit a model, $\hat\theta$, which detects the number of latent groups and classifies latent group membership for each node in $G^{*}$.

### Bootstrapping estimates from $\hat\theta$ over many draws characterizes the latent structure such that number of groups and group status of nodes in $G^{*}$ ~ $G$.

<br>

<br>

<br>

<br>

<br>

<br>





